---
title: "Citing References in Rmarkdown Documents"
subtitle: 'Masters Theses & Graduate Research Projects'
date: "Updated `r format(Sys.Date(), '%d %b %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{timeline}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r}
shiny::includeCSS('vignette.css')
```

# Overview

This vignette outlines various methods for generating and referencing citations within an Rmarkdown document.  Along with the Base-R functions that are available for this purpose, this vignette will also refer to functions from the R packages `RefManageR` and `knitcitations`. Both of these packages have been published to the CRAN and can be installed from within the R console using the code shown in the chunk below.

```{r, eval=FALSE}
install.packages(c('RefManageR', 'knitcitations'))
```

Once installed, you should load the functions from these packages into your current R workspace using

```{r}
library(RefManageR)
library(knitcitations)
```

Now that these packages have been installed and their functions loaded, the rest of this document walks through various use cases for citing references within your thesis or other rmarkdown document.

We'll want to take advantage of the options for each of these packages

```{r}
# RefManageR Options
```



```{r}
# knitcitations Options
cite_options()
```
## The citation workflow

It's important to recognize that citations come in vaious formats and from many different locations.  The general idea is funnel all of your citations to Maybe you already have a file containing hundreds of citations in a bibTeX format have 

# Citing R and R packages

A lot of work goes into making R available for you to use (for free). Therefore, if you use R for your research, you should cite it!  Likewise you should cite any R packages that you use.  The R Core Development team has made it each to generate a citation for R by simply using `citation()` 
# Week 3 - Inform the TPC of an Changes 

- Students, advisors or Department POC will notify the TPC at <a href='mailto:thesis@afit.edu'>thesis@afit.edu</a> of the following:

    - Corrections to the Research Advisor listed on the Projected Graduate spreadsheet

    - Names of students with whom they are doing a group thesis

    - Addition of name(s) to the Projected Graduate List <red>if omitted</red>

    - Removal of name(s) from the Projected Graduate List <red>of students who will not complete their program in the current quarter</red>

# Week 8 - Complete The Thesis Defense

- All Masters Students are required to have their defense completed no later week 8 of their graduating quarter.

# Week 9 - Submit Final Documents

- For Unlimited Distribution Theses & GRP's (Distrbution Statement A)

    - Students will submit their FINAL document and all associated paperwork to their Research Advisor or Department POC

    - All submissions must:

        + Comply with the latest [AFIT Style Guide](http://www.afit.edu/docs/NewAFITStyleGuideJuly2015(2).pdf) 

        + Include a completed SF 298 (located on L drive and incorporated into the document as the last page as well saved as a separate document in student folder)

        + Ensure committee membership page has all committee members listed. 

        + Committee approval signature form with digital signatures placed in student folder. `L:\Thesis-Dissertation\Theses\committee approval signature form (blank).pdf`

        + Completed [WPAFB Form 1420](http://www.wpafb.af.mil/shared/media/document/AFD-160526-016.pdf) with all required digital signatures (Block 10 is student signature; Block 11 is Research Advisor signature; and Block 12 is Department Head/Deputy signature)

- For Limited Distribution Theses & GRP's (Distribution Statements B-F)

    - Students will submit the following documents to their Research Advisor or Department POC <focus>on a labeled CD:</focus>

        - Final thesis/GRP document 

        - Completed distribution Form signed by the research advisor (scan and save as .pdf)

        - Completed SF 298

    - CD labels must include: (label template available in the `forms` folder)

        + Student name
  
        + Designator number

        + <u>Complete</u> Distribution Statement

# Week 10 - Submit Documents to the TPC

- Unlimited Distribution theses & GRP's (Distribution Statement A)

    + Research Advisors or Department POC will upload the following documents to the TPC 

        + <focus>FINAL</focus> Thesis/GRP document with completed SF 298 incorporated into the document as the last page 

        + Completed [WPAFB Form 1420](http://www.wpafb.af.mil/shared/media/document/AFD-160526-016.pdf)

    + NOTE: All documents shall be placed in the following directory `L:\Thesis-Dissertation\Student Submissions\'Student department'\'Student Name'`

    + ENV Distance Learning students will submit Thesis/GRP documents through the [Blackboard SENG 799 Final Thesis Submission Tab](https://afit.blackboard.com/webapps/blackboard/content/listContentEditable.jsp?content_id=_2037686_1&course_id=_9790_1&mode=reset)

    + Research Advisors or Department POC will notify the TPC at <a href='mailto:thesis@afit.edu'>thesis@afit.edu</a> when all documents and forms are uploaded. 
    
    + The TPC will wait to be notified that the documents have been uploaded before submitting the request for PA approval

- Limited Distribution theses/GRPs (Distribution Statements B-F)

    - Research Advisors or Department POC will upload the following documents to the TPC 

        + Completed Document Distribution Form 

        + Digital signature page 

    - Note: all documents shall be uploaded to the following directory `L:\Thesis-Dissertation\Student Submissions\'Student Department'\'Student Name'`

    - ENV Distance Learning students will submit Thesis/GRP documents through the [Blackboard SENG 799 Final Thesis Submission Tab](https://afit.blackboard.com/webapps/blackboard/content/listContentEditable.jsp?content_id=_2037686_1&course_id=_9790_1&mode=reset)

    - Once the documents have been uploaded, research advisors or department POC will notify the TPC at <a href='mailto:thesis@afit.edu'>thesis@afit.edu</a> to set-up an appointment to hand deliver limited document CD for review.
    
- Classified Theses/GRPs 

    + Resident students shall contact Mr. John Banks in the D’Azzo Research Library for instructions
